Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-19 manuscript/manuscript.tex
go back to in-place hyphenation

\hyphenation{val-i-dat-ed}

@@

While there exist automated schemes~\cite{husic-optimized} for cross-validated optimization in the full hyper-parameter space,
we chose to adopt a sequential approach where only the hyper-parameters of the current stage are optimized.
This approach is not only computationally cheaper but allows us to discuss the significance of the necessary modeling choices.

>>>>

@@

While there exist automated schemes~\cite{husic-optimized} for cross-val\-i\-dat\-ed optimization in the full hyper-parameter space,
we chose to adopt a sequential approach where only the hyper-parameters of the current stage are optimized.
This approach is not only computationally cheaper but allows us to discuss the significance of the necessary modeling choices.
